ODGI: understanding pangenome graphs

### 2021-11-04 manuscript/fig_extract_viz_draw_position_untangle.tex
pass through

        The top two reference genomes and 2 haplotypes (HG01952\#2) xgo from left to right, while 5 haplotypes go in the opposite direction, as indicated by the black color on their left.

@@

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, \textit{C4B} gene is missing.

>>>>

        The top two reference genomes and 2 haplotypes (HG01952\#2) go from left to right, while 5 haplotypes go in the opposite direction, as indicated by the black color on their left.

@@

        \textbf{(h)} Visualization of \textit{odgi untangle} output in the C4 pangenome graph: the plots show the copy number status of the sequences in the C4 region with respect to the grch38 reference sequence, making clear, for example, that in HG00438\#2, the \textit{C4B} gene is missing.
